Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-06-13 manuscript/tables&figures.Rmd
Added tables and updated rmd for doing arima ratio instead of difference

>>>>

<!-- \clearpage -->
<!-- ```{r table 5, eval = TRUE, echo=FALSE, warning=FALSE} -->
<!-- # *****this is for if doing arimaratio!!!!***** -->
<!-- library(knitr) -->
<!-- library(kableExtra) -->
<!-- multivar_table <- read.csv("tables_figures/publication/table5_multivariable_models_arimaratio.csv", stringsAsFactors = FALSE, check.names = FALSE) #note: this table is a rearranged version of `tested_traits_best_coeff.csv`. -->
<!-- kable(multivar_table, booktabs = TRUE, caption = "Table 5. Summary of top full models for each drought instance. Models are ranked by AICc, and we show all models whose AICc value falls within 1.0 (dAICc<1) of the best model (bold).", format = 'latex', escape = FALSE) %>% -->
<!--   kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>% -->
<!--   add_header_above(c(" "," "," "," "," ", " ", " ", "xylem porosity" = 2," ", " ")) %>% -->
<!--   pack_rows("", 1, 2, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>% -->
<!--   pack_rows("", 3, 5, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>% -->
<!--   pack_rows("", 6, 7, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>% -->
<!--   pack_rows("", 8, 11, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>% -->
<!--   row_spec(1, bold = T) %>% -->
<!--   row_spec(3, bold = T) %>% -->
<!--   row_spec(6, bold = T) %>% -->
<!--   row_spec(8, bold = T) %>% -->
<!--   kable_styling() -->
<!-- ``` -->
